$\pi$ with leftovers: \\ a mechanisation in Agda

### 2021-01-20 paper/paper.tex
Nail down the explanations on PreCtx, Idxs, Ctx

\todo{definition captions reset textsc}
We keep typing contexts ($\PreCtx$) and usage contexts ($\Ctx$) separate.
The former are preserved throughout typing derivations; the latter are transformed as a result of input, output, and context splits.
\begin{nidefinition}[\textsc{Type} and \textsc{PreCtx}: types and typing contexts]
  A \emph{type} is either a unit type ($\unit$), a base type ($\base{n}$) or a channel type ($\channel{t}{x}$) (first two constructors below).
  \begin{mathpar}
    \datatype
    { }
    {\Type : \Set}
    \; \textsc{Type}

@@

  A \emph{typing context} $\PreCtx_n$ is a length-indexed list of types that is either empty $\constr{[]}$ or the result of appending a type $\Type$ to an existing context.
\end{nidefinition}

\begin{nidefinition}[\textsc{Ctx}: usage contexts]
  A context of indices $\Idxs_n$ is a length-indexed list that is either empty $\constr{[]}$ or the result of appending an index $\Idx$ to an existing context.
  A \emph{usage context} is a context $\Ctx_{idxs}$ indexed by a context of indices $\Idxs_n$ that is either empty $\constr{[]}$ or the result or appending a usage annotation pair $\Usage_{idx}^{\func{2}}$ with index $idx$ to an existing context.
  We use the notation $\type{C}^{\func{2}}$ to stand for a $\type{C} \constr{\times} \type{C}$ pair of input and output multiplicities, respectively.
  Henceforth, we use $\lz$ to denote the multiplicity pair $0 \comma 0$, $\li$ for the pair $1 \comma 0$, $\lo$ for $0 \comma 1$, and $\lio$ for $1 \comma 1$.
  This notation was originally used in the linear \picalc{} \cite{KPT96,Sangio01}.
\end{nidefinition}

>>>>

\todo{definition captions reset textsc}
We keep typing contexts ($\PreCtx$) and usage contexts ($\Ctx$) separate.
The former are preserved throughout typing derivations; the latter are transformed as a result of input, output, and context splits.
\begin{nidefinition}[\textsc{Type} and \textsc{PreCtx}: types and typing contexts]
  A \emph{type} is either a unit type ($\unit$), a base type ($\base{n}$) or a channel type ($\channel{t}{x}$).
  \begin{mathpar}
    \datatype
    { }
    {\Type : \Set}
    \; \textsc{Type}

@@

  A \emph{typing context} $\PreCtx_n$ is a length-indexed list of types that is either empty ($\constr{[]}$) or the result of appending a type $t : \Type$ to an existing context ($\gamma \constr{,} t$).
\end{nidefinition}

\begin{nidefinition}[\textsc{Idxs} and \textsc{Ctx}: contexts of indices and usage contexts]
  A context of indices $\Idxs_n$ is a length-indexed list that is either empty ($\constr{[]}$) or the result of appending an index $i : \Idx$ to an existing context ($idxs \constr{,} i$).
  A \emph{usage context} is a context $\Ctx_{idxs}$ indexed by a context of indices $idxs : \Idxs_n$ that is either empty ($\constr{[]}$) or the result or appending a usage annotation pair $u : \Usage_{idx}^{\func{2}}$ with index $idx : \Idx$ to an existing context ($\Gamma \constr{,} u$).
  We use the notation $\type{C}^{\func{2}}$ to stand for a $\type{C} \constr{\times} \type{C}$ pair of input and output multiplicities, respectively.
  Henceforth, we use $\lz$ to denote the multiplicity pair $0 \comma 0$, $\li$ for the pair $1 \comma 0$, $\lo$ for $0 \comma 1$, and $\lio$ for $1 \comma 1$.
  This notation was originally used in the linear \picalc{} \cite{KPT96,Sangio01}.
\end{nidefinition}
